### 2011-08-19 doc/theses/vitasek/chapter-4-experiments.tex
Thesis: in progress.

@@

TODO graph + interpretation. Graph should have its Y axis in log, stress this fact in the text too

>>>>

\begin{figure}
  \caption{Time vs. Quality}
  \label{image-experiment-time-vs-quality}
  \centering
    \includegraphics[angle=-90, width=\textwidth]{images/experiments/time-vs-quality}
\end{figure}

TODO interpretation

@@

\begin{figure}
  \caption{Time vs. Quality}
  \label{image-experiment-time-vs-quality}
  \centering
    \includegraphics[angle=-90, width=\textwidth]{images/experiments/time-till-optimum}
\end{figure}

TODO interpretation. Graph should has its Y axis in log, stress this fact in the text too
